Response to Reviewers' Comments

### 2025-02-06 paper.tex
Apply latex indent for a cleaner doc
Add some information about geometrical computation

\tablename~\ref{fig:performances} shows a summary of GPU computation times for each method and with these two experiments. 
As detailed in previous sections, all heavy computations in \framework are offloaded to the GPU, while the CPU is minimally involved in physical calculations. This design choice ensures that the CPU remains available for other standard game or simulation tasks, optimizing overall system performance. Therefore, CPU computation times are not considered, as they are negligible compared to GPU ones. 
First, it can be observed that real-time performance is largely achieved, even with \emph{ten-solids}. 
Besides, as most of the computations are performed on the GPU, it can be observed that computation times do not grow linearly with the number of solids. 
Indeed, \framework processes each solid and each FDM grid simulation in parallel.

\begin{figure}[!h]
	\centering
	\begin{tabular}{|p{0.28\columnwidth}|p{0.24\columnwidth}|>{\centering\arraybackslash}p{0.14\columnwidth}|>{\centering\arraybackslash}p{0.14\columnwidth}|}
		\hline
        & & XP 1 & XP 2 \\
        & & (\emph{one-solid}) & (\emph{ten-solids}) \\
		\hline
		Tessendorf's method & Height (\S~\ref{subsec:waterHeight}) & 0.376 & 0.376\\
        \cline{2-4}
		(\S~\ref{sec:oceanWaves}) & Velocity (\S~\ref{subsec:velWater}) & 1.175 & 1.175\\
		\cline{2-4}
		  & Total & 1.551 & 1.551\\
		\hline
		Fluid-to-solid coupling & Geometry (\S~\ref{subsec:geomParam}) & 1.125 & 4.588\\
		\cline{2-4}
        (\S~\ref{sec:fluidToSolidAction}) & Forces (\S~\ref{subsec:forces}) & 0.406 & 3.677\\
		\cline{2-4}
        & Total & 1.531 & 8.265\\
		\hline
		Solid-to-fluid coupling & FDM (\S~\ref{subsec:finiteDifferenceMethod}) & 0.100                    & 0.831                    \\
		\cline{2-4}
        (\S~\ref{sec:solidToFluidAction}) & Mask (\S~\ref{subsec:mask}) & 0.238 & 1.656\\
		\cline{2-4}
        & Total & 0.338 & 2.487\\
		\hline
		\rowcolor{bleuC}\textbf{Total} & & \textbf{3.414} & \textbf{12.297}\\
		\hline
	\end{tabular}
	\caption{%
        GPU computation times in milliseconds for the main parts of \framework. 
        Only GPU execution times is shown, as CPU ones are negligible.}
	\label{fig:performances}
\end{figure}

@@

\begin{align}
\frac{\partial \tilde{h}}{\partial t}(\mathbf{k},t) - \frac{\tilde{\partial}\phi}{\partial y}(\mathbf{k}, 0, t) &=0 \nonumber\\
i\omega(k)\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) - \frac{igk}{\omega(k)} E(\mathbf{k},0)\nonumber\\
 \times \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) &= 0 \nonumber\\
 \omega(k)- \frac{gk}{\omega(k)} &= 0 \nonumber\\
 \omega(k) = \sqrt{gk} \label{equa:relationDispersionDeduce}
\end{align}

>>>>

\tablename~\ref{fig:performances} shows a summary of GPU computation times for each method and with these two experiments.
As detailed in previous sections, all heavy computations in \framework are offloaded to the GPU, while the CPU is minimally involved in physical calculations. This design choice ensures that the CPU remains available for other standard game or simulation tasks, optimizing overall system performance. Therefore, CPU computation times are not considered, as they are negligible compared to GPU ones.
First, it can be observed that real-time performance is largely achieved, even with \emph{ten-solids}. One of the most computationally intensive steps is geometry computation, which presents an opportunity for further optimization. A closer inspection suggests that refining memory access patterns and minimizing warp branch divergence in the GPU kernel could enhance performance and efficiency.
Besides, as most of the computations are performed on the GPU, it can be observed that computation times do not grow linearly with the number of solids.
Indeed, \framework processes each solid and each FDM grid simulation in parallel.
\begin{figure}[!h]
	\centering
	\begin{tabular}{|p{0.28\columnwidth}|p{0.24\columnwidth}|>{\centering\arraybackslash}p{0.14\columnwidth}|>{\centering\arraybackslash}p{0.14\columnwidth}|}
		\hline
		                                  &                                              & XP 1               & XP 2                \\
		                                  &                                              & (\emph{one-solid}) & (\emph{ten-solids}) \\
		\hline
		Tessendorf's method               & Height (\S~\ref{subsec:waterHeight})         & 0.376              & 0.376               \\
		\cline{2-4}
		(\S~\ref{sec:oceanWaves})         & Velocity (\S~\ref{subsec:velWater})          & 1.175              & 1.175               \\
		\cline{2-4}
		                                  & Total                                        & 1.551              & 1.551               \\
		\hline
		Fluid-to-solid coupling           & Geometry (\S~\ref{subsec:geomParam})         & 1.125              & 4.588               \\
		\cline{2-4}
		(\S~\ref{sec:fluidToSolidAction}) & Forces (\S~\ref{subsec:forces})              & 0.406              & 3.677               \\
		\cline{2-4}
		                                  & Total                                        & 1.531              & 8.265               \\
		\hline
		Solid-to-fluid coupling           & FDM (\S~\ref{subsec:finiteDifferenceMethod}) & 0.100              & 0.831               \\
		\cline{2-4}
		(\S~\ref{sec:solidToFluidAction}) & Mask (\S~\ref{subsec:mask})                  & 0.238              & 1.656               \\
		\cline{2-4}
		                                  & Total                                        & 0.338              & 2.487               \\
		\hline
		\rowcolor{bleuC}\textbf{Total}    &                                              & \textbf{3.414}     & \textbf{12.297}     \\
		\hline
	\end{tabular}
	\caption{%
		GPU computation times in milliseconds for the main parts of \framework.
		Only GPU execution times is shown, as CPU ones are negligible.}
	\label{fig:performances}
\end{figure}

@@

\begin{align}
	\frac{\partial \tilde{h}}{\partial t}(\mathbf{k},t) - \frac{\tilde{\partial}\phi}{\partial y}(\mathbf{k}, 0, t) & =0 \nonumber                                \\
	i\omega(k)\left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right) - \frac{igk}{\omega(k)} E(\mathbf{k},0)\nonumber \\
	\times \left(\tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)-\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t)\right)       & = 0 \nonumber                               \\
	\omega(k)- \frac{gk}{\omega(k)}                                                                                 & = 0 \nonumber                               \\
	\omega(k) = \sqrt{gk} \label{equa:relationDispersionDeduce}
\end{align}

### 2025-02-06 review/review.tex
Update the graph with log scale
Add some information about geometrical computation

	      \answer{TODO.}

@@

	      \answer{TODO.}

>>>>

	      \answer{We have added details in the article to clarify the implementation. Geometry computation is one of the most intensive steps, we think that it might comes from uncoalesced memory accesses and warp branch divergence which may contribute to the observed bottleneck.}

@@

	      \answer{We appreciate your suggestion. We have updated Figure 6 to use a logarithmic vertical scale, which significantly improves readability by better separating the data and making the variations clearer.}
